---
title: "assignment-5-kmeans"
output: html_document
date: "2023-10-26"
---

```{r}
library(tidyverse)
library(stats)
library(ggfortify)
library(factoextra)
```

Load the dataset mammal_Sleep.csv into a data frame.
```{r}
sleep <- read.csv("mammalsleep.csv")
```

```{r}
view(sleep)
```

Create a new data frame mammalSleep with sleep_total and sleep_rem.
```{r}
mmsleep <- sleep[,c(7,8)]
```

```{r}
view(mmsleep)
```

Replace NA value with mean
```{r}
mmsleep$sleep_rem[is.na(mmsleep$sleep_rem)] <- mean(mmsleep$sleep_rem,na.rm = TRUE)
view(mmsleep)
```

scale the dataset
```{r}
mmsleep_scale <- scale(mmsleep)
```

```{r}
fviz_nbclust(mmsleep_scale, kmeans, method = "wss") +
  labs(subtitle = "Elbow method")
```

```{r pressure, echo=FALSE}
plot(pressure)
```

```{r}
mmsleep_scale <- scale(mmsleep)
```


Fit a k-means clustering model with 4 clusters to the data subset mammalSleep.
```{r}
model_mmsleep <- kmeans(mmsleep_scale,centers = 4, nstart = 1)
```

cluster plot
boundary around the clusters
```{r}
autoplot(model_mmsleep, mmsleep_scale, frame= TRUE)
```

visualize it in a better way
```{r}
mmsleep.clusters <- model_mmsleep$cluster
```

```{r}
rownames(mmsleep_scale) <- paste(sleep$name,
                               1:dim(sleep)[1],
                               sep = "_")

```


Find the centroids of the clusters in the model on the chart 
```{r}
fviz_cluster(list(data=mmsleep_scale,
                  cluster = mmsleep.clusters))
```
