---
title: "assignment4_dentalservice"
output: html_document
date: "2023-10-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

read csv

```{r}
df_dental <- read.csv("dentalservice.csv")
```
scatter plot to check relation between feature
and target variables

Dentistsvisits and Income
```{r}
df_dental %>% 
  ggplot(aes(DentistVisits, Income)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "DentistVisits", y = "Income",
       title = "DentistVisits vs Income")
```

Price and Income
```{r}
df_dental %>% 
  ggplot(aes(Price, Income)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Price", y = "Income",
       title = "Price vs Income")
```

There is a relatioship between Price and Income. 
As the price increase, the income increase as well

split the dataset
```{r}
set.seed(1)
df_dental$id <- 1:nrow(df_dental)
```

```{r}
view(df_dental)
```

```{r}
train_dental <- df_dental %>% sample_frac(0.80)
```

```{r}
test_dental <- anti_join(df_dental, train_dental,
                       by="id")
```

train the model
```{r}
model5 <- lm (Income ~ Price,
              data = train_dental)
```
```{r}
summary(model5)
```

test the model
```{r}
test_dental$predicted_values <- predict(model5, test_dental)
view(test_dental)
```

calculate the error
```{r}
error <- sqrt(mean(((test_dental$Income) -
                      test_dental$predicted_values))^2)
```

```{r}
print(error)
```
The regression line is positive, and the error is 2.62 close to zero, 
there is a weak relationship between income est price

predict(modelname, dataframe)

```{r}
predict(model5, data.frame(Price=c(50, 90, 200)))
```

prediction of $50 as price gives 66.59 as Income and
prediction of $200 as price gives 296.52 as Income

adding row in dataframe

```{r}
df2 <- df_dental %>%
  add_row(Income = 67, DentistVisits = 0, Price = 50, id = 50)
```

```{r}

df2 <- df2 %>%
 add_row(Income = 297, DentistVisits = 0, Price = 200, id = 51)
```

```{r}
df3 <- tail(df2, 2)
```

Add both new values to the scatter linear graph
```{r}
df2 %>% 
  ggplot(aes(Price, Income)) +
  geom_point() +
  geom_point(data = df3, aes(Price, Income),
             color = "red",
             size = 5) +
  geom_smooth(method = "lm") +
  labs(x = "Price", y = "Income",
       title = "Price vs Income")
```


```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
